---
title: "Precis"
author: "Molly Leavens"
date: "10/15/2018"
output: html_document
---

I am using survey data conducted by Micheal Hiscox (professor in the Gov department) and Mondelez (world's largest chocolate company) of thousands of Ghanian cacao farmers. They conducted the survey twice (2 waves). Once in 2008 and once in 2014.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

A PhD student who helped impliment the survey sent me 5 different CSV files that each have the data formatted differently (and include different parts of the survey). I am first trying to figure out which ones I would like to work it and how they all vary. 

I was also send an R script that "cleans and summarizes the two waves" so I am trying to figure out how and when to use that. This is titeled "my run 004 1 June. R" and I loaded in into this repo. 

```{r,include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
both_waves <- read_csv("farmerData_bothWaves.csv")
wave_2 <- read_csv("Farmer_Survey_withKeyIndicators_wave2.csv")
wave_1 <- read_csv("wave1_Farmer_Survey_Cleaned_with_key_indicators.csv")
wave_1_raw <- read_csv("wave1_raw.csv")
```

After reviewing some summary statistics (and the recently taught setequal function!), I found that two of the surveys are identical (but with a different name) so I removed the duplicate from the repo.

The file titled "both waves" has the same number of observations as the sum of the two individaul wave files (2562 + 2809) but only 153 variables. The inidividual wave files by contrast have 1,945 and 2,845 variables. Still trying to figure out why the difference. The file labeled "wave 1 raw" has the same number of observations as wave_1 but 29 fewer variables. Still trying to figure out why the difference. I was not provided a "wave 2 raw".

I cannot do more summary statistics at this time becuase I am still trying to figure out conceptually which variabels I care about. I cannot assess thousands so it comes down to which could support my theis statement once I turn this analysis into a paper.  

